Seeing Double: Indications From {\it TESS} and {\it Gaia} That PTFO$\,$8-8695b is Not a Planet

### 2020-04-17 paper/ms.tex
paper update

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.5\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Timing residuals for \ptfob\ from a decade of monitoring.}
		Black points are times of ``dips'', minus the indicated linear
		ephemeris.  The $y$-axis is given in units of phase for the
		short-period signal.  The star shows the binned TESS ephemeris.
		``Dips'' have been observed by \citet{van_eyken_ptf_2012},
		\citet{ciardi_followup_2015}, \citet{yu_tests_2015},
		\citet{raetz_yeti_2016}, \citet{onitsuka_multi-color_2017}, and
		\citet{tanimoto_evidence_2020}.  Certain dips ({\it e.g.}, the one
		at phase 0 in mid-2019) are consistent with noise, and were likely
		reported because something was {\it expected}, rather than
		convincingly {\it observed}.  Horizontal dashed lines are drawn at
		$\pm (P_{\rm \ell} - P_{\rm s})/P_{\rm s}$, highlighting what
		could be either a numerical coincidence or an observational bias.
		The orbital phase observed by TESS is consistent with that of
		\citet{tanimoto_evidence_2020}, and quite different from the
		original phase.
		\label{fig:o_minus_c}
	}
\end{figure}

@@

% The main result that both models agree on: the extra power at the
% orbital frequency seems to not be ellipsoidal. Both of these models
% prefer to put the power at 1x the orbital frequency, not 2x the
% orbital frequency! This gives both Aorb0 and Borb0 non-zero, while
% Aorb1 and Borb1 seem to be more consistent with zero.

\section{Plausible Physical Interpretations}

>>>>

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.5\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Timing residuals for \ptfob\ from a decade of monitoring.}
		Black points are times of ``dips'', minus the indicated linear
		ephemeris.  The $y$-axis is given in units of phase for the
		short-period signal.  The star shows the binned TESS ephemeris.
		``Dips'' have been observed by \citet{van_eyken_ptf_2012},
		\citet{ciardi_followup_2015}, \citet{yu_tests_2015},
		\citet{raetz_yeti_2016}, \citet{onitsuka_multicolor_2017}, and
		\citet{tanimoto_evidence_2020}.  Certain dips ({\it e.g.}, the one
		at phase 0 in mid-2019) are consistent with noise, and were likely
		reported because something was {\it expected}, rather than
		convincingly {\it observed}.  Horizontal dashed lines are drawn at
		$\pm (P_{\rm \ell} - P_{\rm s})/P_{\rm s}$, highlighting a
    possible observational bias.  The orbital phase observed by TESS
    is consistent with that of \citet{tanimoto_evidence_2020}, and
    quite different from the original phase.
		\label{fig:o_minus_c}
	}
\end{figure}

@@

\section{Physical Interpretation}

Given the evidence, we believe that PTFO$\,$8-8695 is a binary M dwarf
in which one star shows the ``long'' rotation signal, and the other is
showing ``transient dipping'' that has also been observed in other
young M dwarfs.

Many other young M-dwarf photometric binaries
have been observed in {\it e.g.,} Upper Sco and the Pleiades to show
multiple periods \citep{rebull_usco_2018,stauffer_rotevol_2018}.
Typically, the periods are both rotational modulation.

However, occasionally one or both periods can be ``scallop-shell''
variability, {\it e.g.}, EPIC 203956650 in $\rho$Oph
\citep{rebull_usco_2018}.

There are

The gas in the disks is gone (CITE).
The upper limits on the SED from \citet{yu_tests_2015} imply X, Y, Z.
The stars are therefore presumably no longer ``magnetically locked''
to their disks.
This is consistent with the $\approx$half-day periodicities of both
signals.
In the broader context of rapidly rotating young M-dwarfs, ``magnetic
locking'' causes classical disked T-Tauri stars tend to rotate more
{\it slowly}, and almost none have periods less than two days
\citep[{\it e.g.},][]{rebull_rotation_2020}.

The main physical question is what is causing the ``transient
dipping''. This is an unsolved problem not only for \ptfo\ but also
for an entire class of young rapidly rotating M-dwarfs

The roughly half-day periods of both signals imply that
